---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Merriweather:ital,opsz,wght@0,18..144,300..900;1,18..144,300..900&display=swap');
body {font-family: 'Merriweather', sans-serif;
background-color:#CCC8CA;
}
h1, h2{font-weight: bold;
}
p{
padding: 10px;
}
```

## Headphone usage among students in the OGGB foyer

```{r}
library(tidyverse) 

#Let me first load up my data! 
logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRUzSDuWcGUBSGVSbaJBlaos_hna3TpT16sra3sqHfUaV9A3avnvNWLD0r_DCZHnKiFbN24EErS3c6B/pub?output=csv") 

latest_data = logged_data %>%
  rename(headphone_type = "What is the headphone type?", 
          sitting_with_people = "Is the student sitting with people?", 
          task = "What task is the student doing?", 
          time = "What is the time of day?")%>%
  select(-Timestamp)
```

# Data Analysis in Project 2: How do students use their headphones at UoA? 

My report analyses data which was collected from observing students in the OGGB foyer, University of Auckland, in March 2026.

The data tracks the headphone usage, tasks being performed, and the time of day at which the observation took place.

Let's have a look at the data!

A total of `r length(latest_data$task)` observations were collected. The mean time of observation was at `r round(mean(latest_data$time), 1)` hours into the day. 

```{r}
#Let's see what tasks students are up to at different times
latest_data %>%
  ggplot() +
  geom_bar(aes(x = factor(time), fill = task)) +
  labs(title = "Do tasks change with the time of day?",
       subtitle= "The tasks students are doing at different times in the OGGB foyer, March 2026",
       x = "Time",
       y = "Number of observations",
       fill = "Task")

#Let's see the headphone type for different tasks 
latest_data %>%
  ggplot() +
  geom_bar(aes(x = task, fill = headphone_type)) +
  labs(title = "Headphones types with different tasks",
       subtitle = "The different headphone with different tasks for students in the OGGB foyer, March 2026",
       x = "Task",
       y = "Number of observations",
       fill = "Headphone Type")
```
